---
title: "Text Analysis of The Interpretation of Dreams"
output: html_document
date: "2025-03-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Introduction
This project analyzes Freud’s "The Interpretation of Dreams" using text mining techniques. I will tokenize the text, clean it, and find the most frequent words.

## 2. Libraries
```{r load_libraries}
library(gutenbergr)
library(tidytext)
#library(janeaustenr)
library(tidyr)
library(dplyr)
library(stringr)
library(ggplot2)
library(scales)
```

## 3. Loading the Text
```{r load_text}
dreams_text <- readLines("https://www.gutenberg.org/cache/epub/66048/pg66048.txt", encoding = "UTF-8")
dreams_df <- tibble(text = dreams_text)
```

## 4. Tokenization
```{r tokenize}
tidy_dreams <- dreams_df |> 
  mutate(row = row_number()) |> 
  unnest_tokens(word, text)

View(tidy_dreams)
```

## 5. Removing Stop Words
```{r remove_stopwords}
tidy_dreams <- tidy_dreams |> 
  anti_join(stop_words)

View(tidy_dreams)
```

## 6. Word Frequency
```{r word_count}
tidy_dreams |> count(word, sort = TRUE)
```

## 7. Conclusion
After cleaning the text, the most frequent words are "dream," "dreams," "psychic," "content," and "interpretation". Initially, common stop words like *the" and "of" dominated, but after removal, more meaningful terms emerged.
